Accurate Measurement of Eight Bicycles' Physical Parameters

### 2010-06-02 report/parameterReport.tex
typing more on the report

\documentclass{article}
\usepackage[lmargin=1in,rmargin=1in]{geometry}
\usepackage[colorlinks=true, linkcolor=blue]{hyperref}
\usepackage{graphicx}

@@

\begin{document}
\maketitle
\tableofcontents

\section{Introduction}
D\"{o}hring measured the physical parameters of a scooter~\cite{Dohring1953}.
Singh and Goel measured the physical parameters of a scooter~\cite{Singh1971}.
Roland and Massing measured the physical parameters of a bicycle in much the
same was as presented, including calculations of uncertainty from the indirect
measurement techniques~\cite{Roland1971}. This work is based off of the work
done by Kooijman~\cite{Kooijman2006}. I worked with Jodi Kooijman for a year and
was able to use much of the same apparatus and refine the measurement
technique.
\section{Accuracy}
Error propagation theory was utilized to calculate what the accuracy the
benchmark ideal parameters are based on the measurements taken. If $x$ is a
random variable and is defined as $x=f(u,v,\ldots)$ then the sample variance of
$x$ is defined as
\begin{equation}
    s_x^2 = \frac{1}{N-1}\sum^N_{i=1}
    \left[(u_i - \bar{u})^2\left(\frac{\partial x}{\partial u}\right)^2 +
    (v_i - \bar{v})^2\left(\frac{\partial x}{\partial v}\right)^2 +
    2(u_i - \bar{u})(v_i - \bar{v})\left(\frac{\partial x}{\partial u}\right)\left(\frac{\partial x}{\partial v}\right)
    + \ldots\right]
    \label{eqn:sampleVariance}
\end{equation}
Using the definitions for variance and covariance
Equation~\ref{eqn:sampleVariance} can be simplified to
\begin{equation}
    s_x^2 = s_u^2\left(\frac{\partial x}{\partial u}\right)^2 +
            s_v^2\left(\frac{\partial x}{\partial v}\right)^2 +
            2s_{uv}\left(\frac{\partial x}{\partial u}\right)\left(\frac{\partial x}{\partial v}\right)
            + \ldots
    \label{eqn:variance}
\end{equation}
If $u$ and $v$ are uncorrelated then $s_{uv}=0$. We assume that the all the
random variables hereafter are uncorrelated. Equation~\ref{eqn:variance} can be
used to calculated the variance of all types of functions. The most basic are
functions such as addtion
\begin{eqnarray}
    \label{eqn:addition}
    x &=&  au + bv\\
    s_x &=& a^2s_u^2 + b^2s_v^2
\end{eqnarray}

>>>>

\documentclass{article}

\usepackage[lmargin=1in,rmargin=1in]{geometry}
\usepackage[colorlinks=true, linkcolor=blue]{hyperref}
\usepackage{graphicx}

@@

\begin{document}

\maketitle
\tableofcontents

\section{Introduction}
This work is intended to document the indirect measurement of eight real
bicycles' physical parameters. The physical parameters measured are those that
are needed for the benchmark bicycle model~\cite{Meijaard2007}. The work is
based off of the techiques used to measure the instrumented bicycle in
\cite{Kooijman2006} and \cite{Kooijman2008}. I used the same techniques as
Kooijman to measure a second instrumented bicycle~\cite{Moore2009a}. This
method had low accuracy and the $I_{yy}$ moments of inertia were
not measured for the fork and frame. Furthermore, very little data exists on
the physical parameters of different types of bicycles and this work aims to
provide a small sample of bicycles.

D\"{o}hring measured the physical parameters of a scooter~\cite{Dohring1953}.
Singh and Goel measured the physical parameters of a scooter~\cite{Singh1971}.
Roland and Massing measured the physical parameters of a bicycle in much the
same was as presented, including calculations of uncertainty from the indirect
measurement techniques~\cite{Roland1971}. This work is based off of the work
done by Kooijman~\cite{Kooijman2006}. I worked with Jodi Kooijman for a year and
was able to use much of the same apparatus and refine the measurement
technique.
\section{Accuracy}
Error propagation theory was utilized to calculate what the accuracy the
benchmark ideal parameters are based on the measurements taken. If $x$ is a
random variable and is defined as $x=f(u,v,\ldots)$ then the sample variance of
$x$ is defined as
\begin{equation}
    s_x^2 = \frac{1}{N-1}\sum^N_{i=1}
    \left[(u_i - \bar{u})^2\left(\frac{\partial x}{\partial u}\right)^2 +
    (v_i - \bar{v})^2\left(\frac{\partial x}{\partial v}\right)^2 +
    2(u_i - \bar{u})(v_i - \bar{v})\left(\frac{\partial x}{\partial u}\right)\left(\frac{\partial x}{\partial v}\right)
    + \ldots\right]
    \label{eqn:sampleVariance}
\end{equation}
Using the definitions for variance and covariance
Equation~\ref{eqn:sampleVariance} can be simplified to
\begin{equation}
    s_x^2 = s_u^2\left(\frac{\partial x}{\partial u}\right)^2 +
            s_v^2\left(\frac{\partial x}{\partial v}\right)^2 +
            2s_{uv}\left(\frac{\partial x}{\partial u}\right)\left(\frac{\partial x}{\partial v}\right)
            + \ldots
    \label{eqn:variance}
\end{equation}
If $u$ and $v$ are uncorrelated then $s_{uv}=0$. We assume that the all the
random variables hereafter are uncorrelated. Equation~\ref{eqn:variance} can be
used to calculated the variance of all types of functions. The most basic are
functions such as addtion
\begin{eqnarray}
    \label{eqn:addition}
    x &=&  au + bv\\
    s_x &=& a^2s_u^2 + b^2s_v^2
\end{eqnarray}
